---
title: "Syllabus"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(timeDate)
library(tibble)
library(dplyr)
library(knitr)

# https://www.benlinzmeier.rocks/post/an-rmarkdown-syllabus-template/
# http://svmiller.com/blog/2016/07/r-markdown-syllabus/

library(lubridate) # for submission date of assignments

# library(RefManageR)
# bib <- ReadBib("library.bib")
# myopts <- BibOptions(bib.style = "authoryear", style="latex", first.inits=FALSE, max.names = 20)

# https://www.lmu.de/en/workspace-for-students/abc-study-guide/lecture-periods/index.html
# https://www.ferienwiki.de/feiertage/de/bayern

#This code chunk sets up a table of meeting days for the course.
#You can set days of the week for course meetings (e.g. Monday and Wednesday).
#Semester start and end dates are selected and then university holidays like spring break are specified.
#Days of the week that the course meets. Must be full day name in quotes.
Days <- c("Thursday")
#Semester start date for classes as YYYY/M/D.
SemesterStart <- as.Date("2025/4/15")
#Semester end date for classes as YYYY/M/D.
SemesterEnd <- as.Date("2025/7/19")
#Fall break start and stop date.
WinterBreak <-
  seq.Date(
    from = as.Date("2022/12/23"),
    to = as.Date("2023/1/9"),
    by = "day"
  )
#Spring break start and stop date.
# SpringBreak <-
#   seq.Date(
#     from = as.Date("2022/02/28"),
#     to = as.Date("2022/03/06"),
#     by = "day"
#   )
#Creates a list of days within the semester.
SemesterDays <-
  seq.Date(from = SemesterStart, to = SemesterEnd, by = "day")
#Add day before Thanksgiving.
#Add day before Thanksgiving.
# DayBeforeThnks<-as.Date(holiday(
#     year = getRmetricsOptions("currentYear"),
#     Holiday = c("USThanksgivingDay")))-1
#Full list of holidays that there are no classes including breaks.
Holidays <-
  c(as.Date(holiday(
    year = getRmetricsOptions("currentYear"),
    Holiday = c("USLaborDay", "USThanksgivingDay", "USMLKingsBirthday")
  )), WinterBreak)
#Create a list of semester days excluding holidays.
SemesterDays <- SemesterDays[!SemesterDays %in% Holidays]
#Make dataframe with all semester days.
ClassDays <- data.frame(index = 1:length(SemesterDays))
#Insert dates.
ClassDays$Date <- SemesterDays
#Insert weekday designation.
ClassDays$Weekday <- weekdays(ClassDays$Date)
#Limit to the class meeting days.
MeetingDays <- ClassDays[ClassDays$Weekday %in% Days, ]
#Create numeric list of weeks.
Week <- cut.Date(MeetingDays$Date, breaks = "week")
levels(Week) <- 1:length(levels(Week))
MeetingDays$Week <- Week
MeetingDays$Class <- 1:nrow(MeetingDays)

Lecture_Topic <- c("Concepts", # Class 1
                   "Far-right ideology: from transnational traits to local idiosyncracies", # Class 2
                   "Parties: radical and extreme", # Class 3
                   "Parties: representatives", # Class 4
                   "Parties: voters", # Class 5
                   "Parties: responses and counter-strategies", # Class 6
                   "Movement-parties", # Class 7
                   "Mobilisation and movements", # Class 8
                   "Counter-mobilisation", # Class 9
                   "Movement decline, failure, and demobilisation", # Class 10
                   "Radicalisation", # Class 11
                   "Violence", # Class 12
                   "Online", # Class 13
                   "Studying the far right: methods, ethics, and safety") # Class 14 , 
# 15: "Studying the far right: ethics and safety")
          
links <- c("#class1","#class2","#class3","#class4","#class5","#class6","#class7","#class8","#class9","#class10","#class11","#class12","#class13","#class14")

MeetingDays <- bind_cols(MeetingDays, Lecture = Lecture_Topic)
#### Grade table ####
Grades <- tribble( ~ Grade,
                   ~ Range,
                   "A",
                   "90-100",
                   "B",
                   "80-89",
                   "C",
                   "70-79",
                   "D",
                   "60-69",
                   "F",
                   "< 60")
####Assignment weight table####
Weights <- tribble(
                    ~ Item,
                    ~ Weight,
                    "Writing scaffolding",
                    "20 %",
                    "Semester Project",
                    "25 %",
                    "Labratory Assignments",
                    "20 %",
                    "Midterm Exam",
                    "15 %",
                    "Final Exam",
                    "20 %"
                  )
```



# Recommended prior knowledge
<!-- Empfohlene Vorkenntnisse -->

Students will benefit from familiarity with research literature on political parties, social movements, and/or political violence. But relevant parts of these research fields will be introduced in the course where pertinent. 

# Necessary prerequisites
<!-- Notwendige Voraussetzungen -->

Not applicable.

# Course requirements

The examination credit (*Prüfungsleistung*) in this course depends on your degree programme:

```{r requirements, echo=FALSE, message=FALSE, warning=FALSE}
library(kableExtra)
# col1 <- c("","Attendance & Participation","Presentation","Essay"),
kable(data.frame(
  col1 <- c("","Participation","Presentation","Essay","Exercise","Klausur"),
  col2 <- c("BA main","X","X","X","",""),
  col3 <- c("BA minor (60 ECTS)","X","X","X","",""),
  col4 <- c("BA minor (30 ECTS)","X","X (or Exercise)","","X (or Presentation)",""),
  col5 <- c("Pedagogy","X","X (or Exercise)","","X (or Presentation)","X"),
  col6 <- c("Exchange","X","X","X","","")),
  col.names = NULL, align = c("l","c","c","c","c","c")) %>%
  kableExtra::kable_styling(bootstrap_options = "bordered") %>% 
  # row_spec(1, background = "seagreen1") %>% 
  row_spec(c(3,5), background = "pink") %>% 
  row_spec(c(2,4,6), background = "cadetblue1")
```


## Participation

To receive credit for this course, all students are expected to attend class meetings and participate actively in class discussions. Active participation requires independent preparation, especially [doing the required reading]{style="color:red;"}. Assigned and recommended readings for each session are listed in the [Schedule](../schedule/index.qmd).

## Presentation (*Referat*)

Students that are required by their degree programme to present must give one short (20 minutes maximum) group (2-3 students) presentation of a method of studying a topic within the area of far-right socio-politics. 

A **method** is a system of data collection and analysis. A presentation of a method should introduce the method, explain how (e.g., for what research topics) it is useful for studying far-right socio-politics, and discuss at least one example of applied research. For example, a group could present *regression analysis* by briefly reviewing the logic of regression techniques, explaining that it is useful for detecting correlations in large sets of data, and explaining how Authors X & Y used regression analysis techniques on incidents of far-right violence within a country.

While students may choose any method after conferring with the instructor, the following is a list of methods that would be suitable for presentation: linear regression, qualitative comparative analysis, (comparative) case study design, network analysis, experimental design, content/discourse analysis, quantitative text analysis, process tracing, spatial analysis, ethnography.

<!-- Students that are required by their degree programme to present must give one short (20 minutes maximum) group (2-3 students) presentation of how the far right relates to the European Union and/or EU-level politics. This presentation should be informed by material from Prof. Dr. Berthold Rittberger's lecture (15026 *Vorlesungsübung*: The Political System of the European Union). The presentation should introduce an area of EU politics, **present a piece of research** (i.e., a journal article or research report) **that deals with the far right in this area of EU politics**, and then lead a short class discussion about the conclusions and significance (e.g., for voters in EU elections) of this research and area of political activity. Students may choose any quality published research for their presentation material, though the instructor may suggest students focus on some other piece of research.  -->

Students are responsible for creating their own group and organising their presentation. The date of presentation will be agreed with the instructor and, wherever possible, arranged so that no more than one group presents per class meeting. 

::: {.callout-caution collapse="true"}
## Scoring rubric

```{r pres-rubric, echo=FALSE}
#| message: false
#| warning: false
#| paged-print: false
# Load necessary library
library(dplyr)
library(kableExtra)

rub <- data.frame(
  # block=c("Content", "Content", "Content", "Content", "Form", "Form"),
  criteria=c("<b>1. Introduction</b> <br> - Was the specific method stated? <br> - Were the fundamental concepts necessary for understanding the method explained? <br> - Was it stated what sort of questions/topics the method can address? <br> - Was the sort of data generated/required for the method described? <br> - Was there an overview of the analytical technique(s) of the method?",
             "<b>2. Application to far-right socio-politics</b> <br> - Was it stated how the method can be applied to far-right socio-politics questions/topics? <br> - Were (hypothetical or actual) examples discuss of different possible applications?", 
             "<b>3. Applied research example</b> <br> - Was an applied example of the method presented? <br> - Was the example's research design described enough to understand the analysis? <br> - Was the example's analysis presented (at least in brief)? <br> Did the presentation offer a good critical appraisal of the quality of the research (especially the applied method)?",
             "<b>4. Conclusion</b> <br> - Were the main points of the presentation summarised? <br> - Did the conclusion describe (at least briefly) how one might apply the method? <br> - Were any points for discussion mentioned or questions from the audience answered?",
             "<b>5. Spoken presentation</b> <br> - Were the speakers loud enough to be heard at the back? <br> - Were they <b>speaking to the audience</b>, speaking freely (good) or rather only reading off notes (bad) or reading off the slides (worst)? <br> - Were any points for discussion mentioned or questions from the audience answered?",
             "<b>6. Visual presentation</b> <br> - Were the presentation materials (slides) clear? <br> - Were any graphics shown readable? <br> - Were any slides overcrowded with text?") #, 
  #present=c("","","","","",""),
  # evaluation=c("","","","","","")
)

colnames(rub)<-c(# "Block",
                 "Criteria and Indicators" #,
                 #"yes/no/partial/NA",
                 #"Evaluation")
)

# kable(plan, format = "latex")  # For LaTeX output
# kable(plan, format = "html")   # For HTML output

rub %>% 
  # group_by(Block) %>% 
  kable("html", escape = FALSE) %>% 
  # collapse_rows(1, valign="middle") %>% 
  kable_styling(full_width = FALSE) # %>% 
  # column_spec(1, bold = TRUE) %>% 
  # collapse_rows(1, valign="middle") # %>% column_spec(2, width = "80px") %>% 
  # column_spec(2, width = "120px")

```

:::

## Essay (*Hausarbeit*)

Students that are required by their degree programme to write a final essay will write an analytical data report on a far-right phenomenon, such as voting for far-right parties in Europe (or in a specific country) or far-right protest activity or far-right violence. The report should be 2000-3000 words (excluding citations). It should briefly introduce the subject, briefly discuss relevant research literature, and (particularly important) **should gather and present (in a tablular and/or graphic format) some data relevant to understanding the far-right phenomenon** (e.g., a report on a party might present their election results; a report on a movement might present the protest events they have organised during a specific period of time). Please note that introduction and literature review are to be *brief*. **The intention of this report is for you to gather data and generate analytical insights**. Imagine that you are describing this far-right phenomenon to someone (a policymaker or researcher) with no specific knowledge of it; your job is to provide context briefly, offer specific knowledge, and why that knowledge is important. 

Students are generally free to choose their topic and have it confirmed by the instructor---though the instructor may veto a topic and assign another, or ask the student to choose another. A couple rules apply: (1) **no national-level election data** (if you want to study a party/parties, consider EU-level or regional-level or local-level); (2) **no drawing any data from or citing Statista or other data curation services**. <!-- By the middle of the semester, students should have started their data collection and should submit a draft dataframe: this (most likely) will be an Excel file with your variables in columns and observations in rows. The instructor will check it and offer any necessary guidance about completing data collection. --> Prior to the end of the semester, students intending to write the essay should submit a one-page synopsis that states your topic, lists some relevant research sources, describes the parameters of the data (i.e., variables, number of observations---think of writing up a mini-codebook) and presents a few example rows (i.e., observations), lists any ideas on how to present the data (i.e., how you will visualise it in your report), and identifies any particular points on which you need preliminary feedback. (**This is your chance to get risk-free feedback on your work. Embrace it!**) Feedback on the synopsis may direct students to revise their topic, focus on other sources, and/or reconsider their data approach to their proposed report.

<!-- Deadline for draft dataframe submission: **`r SemesterEnd - (35)`** -->

Deadline for short synopsis submission: **`r SemesterEnd - (21)`**

Deadline for full report submission (including full dataframe): **`r SemesterEnd + (28)`**

Under exceptional circumstances, the instructor may accept late submissions due to unforeseen circumstances. Generally, late submissions will be marked down 0,3 for every two days it is not submitted. If foreseen circumstances make the deadline impossible, please speak to the instructor to make an alternative arrangement. 

An [example data report](../report/index.qmd) is provided on this website. It is a slightly modified version of a previous student's submission and shows an example of a very good data report.

Finally, a suggested (purely voluntary, but perhaps to your ultimate benefit) mode of conducting work on your report: students may find it advantageous to work in [R](https://www.r-project.org/about.html) and [Rstudio](https://posit.co/download/rstudio-desktop/). This is a powerful data management and analysis tool. It combines the capability to import and visualise data, conduct sophisticated analyses, and even present them in nicely formatted documents (whether Word, PDF, or HTML). Students interested in working with datasets in their theses, going on to advanced academic studies, or pursuing a career in research will benefit enormously from engaging with this tool early and often. The course introduction will provide some tips for using this tool. For further information, please turn to the vast material related to R online or inquire with the instructor.

**Once you have read this far: if you send me an email before second class stating your favourite city and what (if any) topics about the far right you are interested in, I will reply with free tips about data and/or sources that might be suitable for a data report.**

::: {.callout-caution collapse="true"}
## Scoring rubric

```{r rep-rubric, echo=FALSE}
#| message: false
#| warning: false
#| paged-print: false
# Load necessary library
library(dplyr)
library(kableExtra)

rubric <- data.frame(
  # block=c("Content", "Content", "Content", "Content", "Form", "Form"),
  criteria=c("<b>1. Introduction</b> <br> - Does the introduction clearly introduce the topic and related data? <br> - Does the introduction briefly state any information or context that is essential to understanding the topic and/or data? <br> - Does the introduction state the aim of the report? <br> - Does the introduction summarise the structure of the report and the main findings? <br> - Was there an overview of the analytical technique(s) of the method?",
             "<b>2. Literature and concepts</b> <br> - Does the report have a section on relevant literature and concepts related to their topic and data? <br> - Does the section provide detailed systematised concept(s) to understand the rest of the data report? <br> - Does the section provide the contextual information necessary to understand the rest of the data report?", 
             "<b>3. Data description</b> <br> - Does the data description explain how the data were collected or created? <br> - Does the data description report the (most important) variables and overall data structure (e.g., one row is an observation of what)? <br> Does the data description provide any necessary descriptive statistics (e.g., number of observations, range/mean/median, missing observations)? <br> - Does the data description reflect on the strengths and weaknesses of the underlying source of the data?",
             "<b>4. Data presentation</b> <br> - Are the data presented in a tabular and graphical format? <br> - Is the presentation readable and readily interpretable (e.g., clear labels, legends)? <br> - Is the presentation directly connected to the analytical discussion?",
             "<b>5. Analytical insights</b> <br> - Does the report discuss (descriptive) analytical insights enabled by presentation of the data and closer inspection of certain data points or collections of data points? <br> - Is the report cautious about the limits of how much we can interpret the data (e.g., how certain can we be of any trends; how plausible is any speculation about causes?)?",
             "<b>6. Conclusion</b> <br> - Does the conclusion summarise the report? <br> - Does it reflect on the shortcomings or limitations of the data and interpretation? <br> - Does it discuss possible ways that this data might be used further (e.g., for thesis research projects, to inform policy discussions)?",
             "<b>7. Form</b> <br> - Is the report well-organised, logically structured, and easy to follow? <br> - Do the different sections clearly, coherently relate to each other? <br> - Is the writing clear, with few if any spelling, typological, grammatical, or syntactical errors?",
             "<b>8. Data</b> <br> - Has the report been submitted with the raw data? <br> - Is the data file clear? <br> - Would the reader be able to replicate the data report using the data file?") #, 
  # present=c("","","","","",""),
  # evaluation=c("","","","","","")
)

colnames(rubric)<-c("Criteria and Indicators")

# kable(plan, format = "latex")  # For LaTeX output
# kable(plan, format = "html")   # For HTML output

rubric %>% 
  # group_by(Block) %>% 
  kable("html", escape = FALSE) %>% 
  # collapse_rows(1, valign="middle") %>% 
  kable_styling(full_width = FALSE) # %>% 
  # column_spec(1, bold = TRUE) %>% 
  # collapse_rows(1, valign="middle") # %>% column_spec(2, width = "80px") %>% 
  # column_spec(2, width = "120px")

```

:::

<!-- ## Exercise (*Übungsaufgabe*) -->

<!-- Students that are required by their degree programme to complete an exercise will write a memo on an assigned far-right actor (e.g., a party, movement, or organisation). The memo topic will be assigned during our 12th class meeting, on **\textcolor{red}{`r MeetingDays$Date[12]`}** and it will be due on the day before our 13th class meeting **\textcolor{red}{`r MeetingDays$Date[13] - 1`}**. Under exceptional circumstances, the instructor may accept late submissions due to unforeseen circumstances. Generally, late submissions will be marked down 0,3 for every two days it is not submitted. If foreseen circumstances make the deadline inconvenient, please speak to the instructor to make an alternative arrangement.  -->

<!-- The memo should be 1000-2000 words. It should provide a basic description of the far-right actor and any important context. It should gather and present (in a table and/or graphic format) some data relevant to understanding the far-right actor (e.g., a memo on a party might present their election results in the last five national elections; a memo on a movement might present the protest events they have organised during a specific period of time). Imagine that you are describing this far-right actor to someone (a policymaker or researcher) with no specific knowledge of it; your job is to provide context, specific knowledge, and why that knowledge is important.  -->

<!-- Possible far-right actors: Reichsbürger,  -->

<!-- ## Klausur -->

# Useful books and sources of information.

1. Mudde, C. (2019). *The far right today*. John Wiley & Sons.

2. Ashe, S. D., Busher, J., Macklin, G., & Winter, A. (Eds.). (2020). *Researching the Far Right: Theory, Method and Practice*. London: Routledge.

3. Virchow, F. (2017). *Handbuch Rechtsextremismus*. Wiesbaden: Springer VS.

4. Mudde, C. (2002). *The Ideology of the Extreme Right*. Manchester: Manchester University Press.

# Student conduct

## Plagiarism

Plagiarism is when ideas and words from others are presented as if they are one's own. It does not matter from which source (e.g., a book, magazine, newspaper, or the internet) the ideas and text came from or whether it is a large or small piece or whether it is copied verbatim or rephrased. The only consequential point is whether the original source is correctly cited or not.

